Cosmological constraints from the redshift dependence of the volume effect using the galaxy 2-point correlation function across the line-of-sight

### 2017-04-03 draft/draft3.1_cris.tex
updates

\author{Xiao-Dong Li, Changbom Park, }
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cristiano G. Sabiu\altaffilmark{1}, Hyunbae Park, }
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
%\author{David H. Weinberg,}
%\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
%\author{Donald P. Schneider,}
%\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
%University Park, PA 16802 }
%\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
%University Park, PA 16802 }
\author{Cheng Cheng, }
\affil{Kavli Institute for Theoretical Physics China, Institute of Theoretical Physics, Chinese Academy of Sciences, Zhong Guan Cun Street 55\#, Beijing, 100190, P.R. China}
\affil{University of Chinese Academy of Sciences, P.R. China}
\author{Juhan Kim,}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\and
\author{Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}

@@

\begin{abstract}
We propose to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, to constrain cosmological parameters.
When an incorrect set of parameters is assumed for the coordinate transformation from redshift space to comoving space, 
it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
As a result, we observe a redshift-dependent rescaling of the measured $\xi(r_{\bot})$.
Using mock galaxy catalogues (containing hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the $\xi(r_{\bot})$ shape, as a function of scale,
is sensitive to the adopted cosmological parameters. 
% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
However, it is relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the effect of redshift space distortions.
Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
The method could be applicable to future large scale structure surveys, especially photometric surveys such as DES, LSST, 
to derive tight cosmological constraints.
This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
as a strategy to constrain cosmological parameters using redshift-invariant physical quantities;
they are all powerful in constrain cosmology and have a lot of merits,
e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
does not require accurate modeling of galaxy clustering,
and are applicable on relative small clustering scales.
\end{abstract}

@@

The discovery of cosmic acceleration \citep{Riess1998,Perl1999} implies the existence of a ``dark energy'' component in the Universe 
or the breakdown of Einstein's gravity theory on cosmological scales \citep[see ][for a recent review]{2012IJMPD..2130002Y}.
The theoretical explanation and observational probe of cosmic acceleration has attracted 
tremendous effort in the last two decades and are still far from well understood or accurately measured \citep{SW1989,Li2011,DHW2013}.
%, but its properties still remain far from accurately known and its nature still remains mystery. 
%The simplest and currently favored solution is the additional field called dark energy which has negative pressure and is spatially homogeneous.
%The simplest explanation for dark energy is that it is a cosmological constant or vacuum energy, with constant equation of state (EoS) $w = -1$.

@@

%As one geometrical effect of cosmological parameters on LSS,  
When an incorrect cosmological model is assumed for the coordinate transformation from redshift space to comoving space,
geometric distortions are produced in the constructed galaxy distribution. 
These distortions include the ``volume effect'' which is the mis-scaling of the size of structures,
and the Alcock-Paczynski (AP) effect, the shape distortion induced by the fact that distances along and perpendicular to the line of sight are fundamentally different.
%Measuring the ratio of galaxy clustering in the radial and transverse directions, provides a probe of the Alcock-Paczynski (AP) effect \citep{AP1979}.
%There have been a series of works studying the application of the AP test to the LSS

@@

Although there have also been alternative approaches using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
Methods proposed to measure the volume effect include the number counting of 
galaxy clusters \citep{PS1974,VL1996}, the topology of LSS \citep{topology},
the BAO scale \citep{EHT1998,BG03,SE03},
and the shape of 2pCF and power spectrum \citep{Sanchez2006,Sanchez2009}.

@@

\cite{Li2014} attempted to use the {\it galaxy density gradient field} 
to characterize the redshift evolution of the LSS distortion. 
We tested the idea on the Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
showing that the redshift evolution of the gradient field 
can be used to infer unbiased constraints on cosmological parameters and that it is, largely, insensitive to RSD.
The same topic was revisited in \cite{Li2015}, 
using a slightly modified version of the usual anisotropic galaxy two-point correlation function (2pCF), $\xi(\mu)$, 
where $\mu\equiv \cos \theta$ and $\theta$ is the angle between the connection of the galaxy pairs and the line of sight direction.
When an incorrect cosmological model is adopted, 
the shape of $\xi(\mu)$ is altered due to the anisotropic distortion of the LSS (the AP effect), 
and the amplitude is shifted due to the change in the comoving volume elements;
both effects have significant redshift dependence.
Although the RSD effect significantly distorts $\xi(\mu)$, 
it exhibits much less redshift evolution.
The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependence of the AP effect, 
and we arrive at tight cosmological constraints competitive with the mainstream probes of SNIa, BAO, and CMB.

In this paper we continue our exploration of this strategy and present 
a new method using the redshift evolution of the shape of the 2-point correlation function across the line-of-sight as a function of radial scale, $\xi(r_{\bot})$,
to constrain cosmology.
A wrongly adopted cosmology results in {\it redshift-dependent mis-scaling} of the galaxy distribution,
which leads to redshift-evolution of the shape of $\xi(r_{\bot})$.
The signal is sensitive to the cosmological parameters but relatively insensitive to the other effects such as the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We apply our method to HR4 mock catalogues, using hundreds of millions of galaxies at redshifts $0\leq z\leq2$
and develop the statistical procedure to constrain cosmological parameters.

@@

\begin{figure*}
   \centering{
   %\includegraphics[height=5.9cm]{fig8_0.eps}
   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
   %\includegraphics[width=16cm]{fig2.eps}
   %\includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
   \includegraphics[width=16cm]{fig2_0.eps}
   }
   \caption{\label{fig_scatter}
  The 2D distribution of a $260\times130\times105 (h^{-1}{\rm Mpc})^3$ subsample of HR4 mock galaxies, 
  at redshifts 0.5, 1, 1.5 and 2.
  Left and right panels show the $x$, $y$ coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
  and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$, respectively.
  The growth of structure strengths the clustering and make structures more compact at lower redshift.
  When the wrong cosmology is adopted, the covmoving distances are mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$, respectively,  leading to a clear redshift evolution of the sizes of structures.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

Although the change of amplitude could be a more significant cosmological consequence 
than the alteration of shape,
it is mixed with the other effects; 
the growth of structure and a larger galaxy bias can also lead to a stronger clustering and thus an enhanced amplitude.
%it is more difficult to 
%But this phenomenon can also appear in case of gravitational growth of structure or increasing of bias,
%so we will not make use of it to do cosmological constraint.
In order to reliably extract the cosmological information, 
we just utilize the redshift evolution of the 2pCF shape, 
which is less affected by other factors.
%which is as a signal suggesting that the assumed cosmological parameters are wrong.

@@

Similar to RSD, redshift errors of galaxies
also results in fuzzy boundaries of redshift shells
Thankfully, there are some methods for mitigating this effect in photometric surveys using pair-center binning \citep{2010MNRAS.407..520N}.

@@

Finally, the fourth row of the Figure displays the 
redshift evolution in case of using samples with constant number density $\bar n=7.3\times 10^{-3} {\rm Mpc}^{-3}h^3$, 
with the RSD effect considered. %(the error bar is a bit larger since for an illustration purpose we only do the computation for 1/30 of the whole sample).
We see the redshfit evolution of $\hat \xi_{r_\perp}$ is as small as $\lesssim3\%$.

@@

In summary, we aim to minimise the redshift evolution of the shape of the normalised angular 2pcf; 
the shape change is dramatic when considering a cosmology much deviated from the fiducial model.
However even in the case of the correct cosmology there remains a small signal, due to growth of structures, RSD and galaxy bias. 
These systematics are removed with the aid of simulations.
The procedure of the correction of systematics is similar to what was implemented in our previous papers \cite{Li2014,Li2015,Li2016}.

The systematics are estimated from a simulation conducted using a particular cosmology. 
There could be a bias in the estimation if the simulation cosmology is different from the truth. 
The bias would not be serious if the simulation cosmology turns out to be consistent with the best-fit cosmological parameters obtained from the analysis \cite{Li2016}. 
In the case that there is a large discrepancy between the simulation cosmology and the best-fit cosmology, one needs to adjust the simulation cosmology and re-do the analysis.

@@

The third row of Figure \ref{fig_sys} shows that, 
if having a large difference in bias between the samples,
there is a large systematic variation on small scales. 
This means that an accurate modelling of systematics from simulations is required. 
To avoid the possible difficulty, one can conduct the analysis using a volume-limited sample, 
where the redshift evolution of galaxy properties is small and the systematic effect from RSD and galaxy bias is also small,
as shown by the fourth row of Figure \ref{fig_sys}.

@@

We do not consider the systematic effects in case of non-standard cosmological scenarios such as modified gravity and warm dark energy. 
These topics go beyond the scope of this work, and they are worthy future investigations.

@@

Adopting the correct cosmological model will result in minimal evolution of the normalised 2pCF.
Thus we proceed to construct a quantitative likelihood estimator that reflects this property.
The procedure here is very similar to \cite{Li2014,Li2015,Li2016}.
We compare the high redshift $\hat\xi_{r_\perp}$ and the lowest redshift measurement,
\begin{equation}
 \delta \hat{\xi_{r_\perp}}(z_i,z_1) \equiv \hat{\xi_{r_\perp}}(z_i) - \hat{\xi_{r_\perp}}(z_1),
\end{equation}
and design the likelihood function to quantify
the redshift evolution of $\hat\xi_{r_\perp}$:
\begin{equation}\label{eq:chisq1}
\chi^2\equiv \sum_{i=2}^{n_{z}} \sum_{j_1=1}^{n_{r}} \sum_{j_2=1}^{n_{r}} {\bf p}(z_i,r_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,r_{j_2}),
\end{equation}
where $n_z$ is the number of redshifts which is 5 in this analysis, 
$n_r$ is number of binning in $\hat{\xi}_{r_\perp}(r_\perp)$,
which is 35 since we have $r_\perp$ bins 
with width $1h^{-1}\rm Mpc$ in a range of $5h^{-1}{\rm Mpc}\leq r_\perp\leq 40h^{-1}{\rm Mpc}$.
${\bf p}(z_i,r_{j})$ is the redshift evolution of the correlation function shape with systematic effects subtracted
\begin{eqnarray}\label{eq:bfp}
 {\bf p}(z_i,r_{j}) \equiv&\ \delta \hat{\xi_\perp}(z_i,z_1,r_j) - \delta \hat{\xi}_{r_\perp,\rm sys}(z_i,z_1,r_j)
\end{eqnarray}
${\bf Cov}_i$ is the covariance matrix estimated from the ${\bf p}(z_i,r_{j})$ measured from 120 subsamples.
%It is difficult to conduct the 2pCF of the whole snapshot box with hundreds of millions of galaxies.
%We split the box into 120 subsamples with $X,Y,Z$ sizes of $1575h^{-1}{\rm Mpc},1575h^{-1}{\rm Mpc}, 105h^{-1}{\rm Mpc}$
%and measure the angular 2pCF in the $X-Y$ plan in these subsamples. 
%The average of the 2pCFs are taken as the 2pCF of the whole box.
%The covariance matrix is also estimated from the redshift evolution of these subsamples.
As mentioned previously, for a robust estimation of the covariance matrix, 
we always compare slices at different locations to 
include the cosmic variance.

@@

So far we simply follow the convention of \cite{Li2016} and adopts $5\hMpc <s< 40\hMpc$. 
As discussed in the \S 4.3.3, one may want to avoid large systematics in the non-linear regime. 
In this case one can adopt $20\hMpc<s<40\hMpc$,
which significantly reduces the systematic effects while not much weaken the power of the final constraints,
as shown by the lower left panel of Figure \ref{fig_contours}.

@@

We have developed a method for constraining certain cosmological parameters by measuring the redshift evolution of the shape of the galaxy correlation function across the line-of-sight, $\hat \xi_{r_\perp}$.
We found that a wrongly adopted cosmology results in a redshift-dependent mis-scaling in the constructed galaxy distribution,
which in turn leads to a redshift-dependent rescaling of $\hat \xi_{r_\perp}(r_\perp)$.
The redshift dependent effect is sensitive to cosmology while being relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We tested our method on the HR4 mock galaxies having 457, 406, 352, 306 and 228 million galaxies at redshifts 0, 0.5, 1, 1.5, 2.
Analyzing the redshift evolution of $\hat \xi_{r_\perp}(r_\perp)$ 
on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$.

@@

In our early work of \cite{Li2015,Li2016}, 
we proposed to use the angular-dependence of the galaxy clustering to apply an AP test and derive cosmological constraints. 
In contrast, in this work we focus on the scale-dependence of the clustering. 
The two methods focus on different parts of the clustering information, and the constraints derived from the them should be fairly independent.
But it is still suggested to have an estimation of the covariance between them in case one is using both methods to do an analysis. 
An alternative way is to investigate the redshift evolution of the correlation map $\xi(s,\mu)$ as a function of both scale and direction, which captures all the information.

@@

%\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
%Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564

>>>>

\author{Xiao-Dong Li, Changbom Park, }
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cristiano G. Sabiu\altaffilmark{1}, Hyunbae Park, }
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
%\author{David H. Weinberg,}
%\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
%\author{Donald P. Schneider,}
%\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
%University Park, PA 16802 }
%\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
%University Park, PA 16802 }
\author{Cheng Cheng, }
\affil{Kavli Institute for Theoretical Physics China, Institute of Theoretical Physics, Chinese Academy of Sciences, Zhong Guan Cun Street 55\#, Beijing, 100190, P.R. China}
\affil{University of Chinese Academy of Sciences, P.R. China}
\author{Juhan Kim,}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
\and
\author{Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}

@@

\begin{abstract}
We propose to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, to constrain cosmological parameters.
When an incorrect set of cosmological parameters is assumed for transforming galaxy redshifts to comoving distances, 
it produces {\it redshift-dependent mis-scaling} in the galaxy distribution.
As a result, we observe a redshift-dependent rescaling in the measured $\xi(r_{\bot})$.
Using mock galaxy catalogues (containing hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the $\xi(r_{\bot})$ shape, as a function of scale,
is sensitive to the adopted cosmological parameters. 
% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
However, it is relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the effect of redshift space distortions.
Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
This method could be applicable to future large scale structure surveys, especially photometric surveys such as DES, LSST, 
to derive tight cosmological constraints.
This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
as a strategy to constrain cosmological parameters using redshift-invariant physical quantities.
They are all powerful in constraining cosmology and have many merits,
e.g., they are less affected by the systematic effects induced by non-linear clustering or RSD,
they do not require accurate modeling of galaxy clustering,
and are applicable on relatively small clustering scales.
\end{abstract}

@@

The discovery of cosmic acceleration \citep{Riess1998,Perl1999} implies the existence of a ``dark energy'' component in the Universe 
or the breakdown of Einstein's gravity theory on cosmological scales \citep[see ][for a recent review]{2012IJMPD..2130002Y}.
The theoretical explanation and observational probes of cosmic acceleration have attracted 
tremendous attention in the last two decades and are still far from being well understood or accurately measured \citep{SW1989,Li2011,DHW2013}.
%, but its properties still remain far from accurately known and its nature still remains mystery. 
%The simplest and currently favored solution is the additional field called dark energy which has negative pressure and is spatially homogeneous.
%The simplest explanation for dark energy is that it is a cosmological constant or vacuum energy, with constant equation of state (EoS) $w = -1$.

@@

When an incorrect cosmological model is assumed when transforming galaxy redshifts to comoving distances,
geometric distortions are produced in the resultant galaxy distribution. It should be noted that this effect is not related to galaxy peculiar velocities which could cause redshift space distortions.
The distortions due to coordinate transforms include the ``volume effect'' which is the mis-scaling of the size of structures,
and the Alcock-Paczynski (AP) effect, the shape distortion induced by the fact that distances along and perpendicular to the line of sight are fundamentally different.
%Measuring the ratio of galaxy clustering in the radial and transverse directions, provides a probe of the Alcock-Paczynski (AP) effect \citep{AP1979}.
%There have been a series of works studying the application of the AP test to the LSS

@@

However, there have also been alternative approaches in utilising the AP effect using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
Methods proposed to measure the volume effect include the number counting of 
galaxy clusters \citep{PS1974,VL1996}, the topology of LSS \citep{topology},
the BAO scale \citep{EHT1998,BG03,SE03},
and the shape of 2pCF and power spectrum \citep{Sanchez2006,Sanchez2009}.

@@

\cite{Li2014} attempted to use the {\it galaxy density gradient field} 
to characterize the redshift evolution of the large scale galaxy distribution. 
We tested the idea on the Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
showing that the redshift evolution of the gradient field 
can be used to infer unbiased constraints on cosmological parameters and that it is, largely, insensitive to RSD.
The same topic was revisited in \cite{Li2015}, 
using a slightly modified version of the usual anisotropic galaxy two-point correlation function (2pCF), $\xi(\mu)$, 
where $\mu\equiv \cos \theta$ and $\theta$ is the angle between the connection of the galaxy pairs and the line of sight direction.
When an incorrect cosmological model is adopted, 
the shape of $\xi(\mu)$ is altered due to the anisotropic distortion of the LSS (the AP effect), 
and the amplitude is shifted due to the change in the comoving volume elements;
both effects have significant redshift dependence.
Although the RSD effect significantly distorts $\xi(\mu)$, 
it exhibits much less redshift evolution.
The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependence of the AP effect, 
and we arrive at tight cosmological constraints competitive with the mainstream probes of SNIa, BAO, and CMB.

In this paper we continue our exploration of this strategy and present 
a new method using the redshift evolution of the shape of the galaxy 2pCF across the line-of-sight as a function of radial scale, $\xi(r_{\bot})$,
to constrain cosmology.
A wrongly adopted cosmology results in {\it redshift-dependent mis-scaling} of the galaxy distribution,
which leads to redshift-evolution of the shape of $\xi(r_{\bot})$.
The signal is sensitive to the cosmological parameters but relatively insensitive to the other effects such as the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We apply our method to HR4 mock catalogues, using hundreds of millions of galaxies at redshifts $0\leq z\leq2$
and develop the statistical procedure to constrain cosmological parameters.

@@

\begin{figure*}
   \centering{
   %\includegraphics[height=5.9cm]{fig8_0.eps}
   %\includegraphics[height=5.9cm]{fig8_wrongcos_0.eps}
   %\includegraphics[width=16cm]{fig2.eps}
   %\includegraphics[width=16cm,natwidth=8,natheight=14]{fig2.pdf}
   \includegraphics[width=16cm]{fig2_0.eps}
   }
   \caption{\label{fig_scatter}
  The 2D distribution of a $260\times130\times105 (h^{-1}{\rm Mpc})^3$ subsample of HR4 mock galaxies, 
  at redshifts 0.5, 1, 1.5 and 2.
  Left and right panels show the $x$, $y$ coordinates computed using the ``correct'' parameters $\Omega_m=0.26,\ w=-1$ 
  and a set of wrong cosmological parameters $\Omega_m=0.05,\ w=-1.5$, respectively.
  The growth of structure strengths the clustering and make structures more compact at lower redshift.
  When the wrong cosmology is adopted, the comoving distances are mis-scaled and over-estimated by $25.6\%,47.3\%,62.2\%,71.7\%$ at redshifts of $0.5,1.0,1.5,2.5$, respectively,  leading to a clear redshift evolution of the sizes of structures.
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

Although the change of amplitude could be a more significant cosmological consequence 
than the alteration of shape,
it is mixed with the other effects; i.e.
the growth of structure and a larger galaxy bias can also lead to a stronger clustering and thus an enhanced amplitude.
%it is more difficult to 
%But this phenomenon can also appear in case of gravitational growth of structure or increasing of bias,
%so we will not make use of it to do cosmological constraint.
In order to reliably extract the cosmological information, 
we just utilize the redshift evolution of the 2pCF shape, 
which is less affected by these complicated factors.
%which is as a signal suggesting that the assumed cosmological parameters are wrong.

@@

Similar to RSD, redshift errors of galaxies
also results in fuzzy boundaries of redshift shells.
Thankfully, there are some methods for mitigating this effect in photometric surveys using, for example, pair-center binning \citep{2010MNRAS.407..520N, 2011MNRAS.415.2193R}.

@@

Finally, the fourth row of the Figure displays the 
redshift evolution in case of using samples with constant number density $\bar n=7.3\times 10^{-3} {\rm Mpc}^{-3}h^3$, 
with the RSD effect considered. %(the error bar is a bit larger since for an illustration purpose we only do the computation for 1/30 of the whole sample).
We see the redshift evolution of $\hat \xi_{r_\perp}$ is as small as $\lesssim3\%$.

@@

In summary, we aim to minimise the redshift evolution of the shape of the normalised  2-point correlation function across the line-of-sight; 
the shape change is dramatic when considering a cosmological model significantly different from the fiducial model.
However even in the case of the correct cosmology there remains a small signal, due to growth of structures, RSD and galaxy bias. 
These systematics are removed with the aid of simulations.
The procedure of the correction of systematics is similar to what was implemented in our previous papers \cite{Li2014,Li2015,Li2016}.

The systematics are estimated from a simulation conducted using a particular cosmology. 
Thus there could be a bias in their estimation if the simulation cosmology is different from the true cosmological model/. 
The bias would not be serious if the simulation cosmology is consistent with the best-fit cosmological parameters obtained from the analysis \cite{Li2016}. 
In the case that there is a large discrepancy between the simulation cosmology and the best-fit cosmology, one needs to adjust the simulation cosmology and re-do the analysis.

@@

The third row of Figure \ref{fig_sys} shows that, 
if having a large difference in galaxy bias between the samples,
there is a large systematic variation on small scales. 
This means that accurate modelling of systematics from simulations is required. 
In an effort to mitigate this problem, one can conduct the analysis using a volume-limited galaxy sample, 
where the redshift evolution of galaxy properties is small and the systematic effect from RSD and galaxy bias is also small,
as shown by the fourth row of Figure \ref{fig_sys}.

@@

We do not consider the systematic effects in case of non-standard cosmological scenarios such as modified gravity and warm dark energy. 
These topics go beyond the scope of this work, however they are worthy future investigations.

@@

Adopting the correct cosmological model will result in minimal evolution of the normalised 2pCF.
Thus we proceed to construct a quantitative likelihood estimator that reflects this property.
The procedure here is very similar to \cite{Li2014,Li2015,Li2016}.
We compare the high redshift $\hat\xi_{r_\perp}$ and the lowest redshift measurement,
\begin{equation}
 \delta \hat{\xi_{r_\perp}}(z_i,z_1) \equiv \hat{\xi_{r_\perp}}(z_i) - \hat{\xi_{r_\perp}}(z_1),
\end{equation}
and design the likelihood function to quantify
the redshift evolution of $\hat\xi_{r_\perp}$:
\begin{equation}\label{eq:chisq1}
\chi^2\equiv \sum_{i=2}^{n_{z}} \sum_{j_1=1}^{n_{r}} \sum_{j_2=1}^{n_{r}} {\bf p}(z_i,r_{j_1}) ({\bf Cov}_{i}^{-1})_{j_1,j_2}  {\bf p}(z_i,r_{j_2}),
\end{equation}
where $n_z$ is the number of redshifts bins, which is 5 in this analysis, 
$n_r$ is number of binning in $\hat{\xi}_{r_\perp}(r_\perp)$,
which is 35 since we have $r_\perp$ bins 
with width $1h^{-1}\rm Mpc$ in a range of $5h^{-1}{\rm Mpc}\leq r_\perp\leq 40h^{-1}{\rm Mpc}$.
${\bf p}(z_i,r_{j})$ is the redshift evolution of the correlation function shape with systematic effects subtracted
\begin{eqnarray}\label{eq:bfp}
 {\bf p}(z_i,r_{j}) \equiv&\ \delta \hat{\xi_\perp}(z_i,z_1,r_j) - \delta \hat{\xi}_{r_\perp,\rm sys}(z_i,z_1,r_j)
\end{eqnarray}
${\bf Cov}_i$ is the covariance matrix estimated from the ${\bf p}(z_i,r_{j})$ measured from 120 subsamples.
%It is difficult to conduct the 2pCF of the whole snapshot box with hundreds of millions of galaxies.
%We split the box into 120 subsamples with $X,Y,Z$ sizes of $1575h^{-1}{\rm Mpc},1575h^{-1}{\rm Mpc}, 105h^{-1}{\rm Mpc}$
%and measure the angular 2pCF in the $X-Y$ plan in these subsamples. 
%The average of the 2pCFs are taken as the 2pCF of the whole box.
%The covariance matrix is also estimated from the redshift evolution of these subsamples.
As mentioned previously, for a robust estimation of the covariance matrix, 
we always compare slices at different locations to 
include the cosmic variance.

@@

So far we simply follow the convention of \cite{Li2016} and adopt $5\hMpc <s< 40\hMpc$ as our analysis scale. 
As discussed in the \S 4.3.3, one may want to avoid large systematics in the non-linear regime. 
In this case one may adopt $20\hMpc<s<40\hMpc$,
which significantly reduces the systematic effects but does not degrade the power of the parameter constraints,
as shown by the lower left panel of Figure \ref{fig_contours}.

@@

We have developed a method for constraining certain cosmological parameters by measuring the redshift evolution of the shape of the galaxy 2pCF across the line-of-sight, $\hat \xi_{r_\perp}$.
We found that a wrongly adopted cosmology results in a redshift-dependent mis-scaling in the constructed galaxy distribution,
which in turn leads to a redshift-dependent rescaling of $\hat \xi_{r_\perp}(r_\perp)$.
The redshift dependent effect is sensitive to cosmology while being relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We tested our method on the HR4 mock galaxies having 457, 406, 352, 306 and 228 million galaxies at redshifts 0, 0.5, 1, 1.5, 2.
Analyzing the redshift evolution of $\hat \xi_{r_\perp}(r_\perp)$ 
on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$.

@@

In our early work of \cite{Li2015,Li2016}, 
we proposed to use the angular-dependence of the galaxy clustering to apply an AP test and derive cosmological constraints. 
In contrast, in this work we focus on the scale-dependence of the clustering. 
The two methods focus on different parts of the clustering information, and the constraints derived from the them should be fairly independent.
However, it is advisable to have an estimation of the covariance between them in the case there one is using both methods in combination.
An alternative way is to investigate the redshift evolution of the correlation map $\xi(s,\mu)$ as a function of both scale and direction, which captures all the information.

@@

%\bibitem[Ross et al.(2012)]{2012MNRAS.424..564R} 
%Ross, A.J., Percival, W.J., \& S{\'a}nchez, A.G. et al.\ 2012, MNRAS, 424, 564 
\bibitem[Ross et al.(2011)]{2011MNRAS.415.2193R} Ross, A.~J., Percival, W.~J., Crocce, M., Cabr{\'e}, A., \& Gazta{\~n}aga, E.\ 2011, \mnras, 415, 2193
